Type Refinements for the Working Class

### 2015-11-11 paper.tex
Switch to pdflatex; change fonts
Make colors conditional; add (conditional) remark explaining mode colors

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{lualatex-math}
%\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{url}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{xunicode}

\definecolor{dark-gray}{gray}{0.20}

% fonts
\usepackage[
  activate={true,nocompatibility},
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

% make lualatex play nice with agda
\makeatletter
\ifluatex%
   \newwrite\CATCHPATCHOUT%
\fi
\def\CatchFBT@Fin@l#1[#2]{%
   \begingroup%
      \endlinechar\m@ne\makeatletter #2%
      \ifluatex%
         \immediate\openout\CATCHPATCHOUT=\jobname.catchpatch%
         \immediate\write\CATCHPATCHOUT{\CatchFBT@tok{\the\CatchFBT@tok}}%
         \immediate\closeout\CATCHPATCHOUT%
         \@@input\jobname.catchpatch%
      \else%
      \scantokens\expandafter{%
         \expandafter\CatchFBT@tok\expandafter{\the\CatchFBT@tok}}%
      \fi%
      \CatchFBT@IsAToken{#1}%
         {\global#1\expandafter{\the\CatchFBT@tok}}%
         {\xdef#1{\the\CatchFBT@tok}}%
      \ifx\CatchFBT@tok#1\else\global\CatchFBT@tok{}\fi%
   \endgroup%
}% \CatchFBT@Final
\makeatother

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\numberwithin{equation}{section}

\def\IModeColorName{MidnightBlue}
\def\OModeColorName{Maroon}

@@

@@

\newcommand\RefinesCtxNil{\sqsubset^\star_{\mathsf{nil}}}
\newcommand\RefinesCtxSnoc{\sqsubset^\star_{\mathsf{snoc}}}

@@

\begin{thm}[Weakening]
  If $\Refines{\Phi}{\phi}{\tau}$, then $\Refines{\Phi,u:\psi}{\phi}{\tau}$ (supposing
  $\NotIn{u}{\Dom\Phi}$ and $\Refines{\Phi}{\psi}{\sigma}$).
\end{thm}
\begin{proof}
  This follows trivially from the rule $\RefinesCtxSnoc$ and the canonical renaming
  $\Upsilon\hookrightarrow\Upsilon,u:\sigma$.
\end{proof}

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{url}

\usepackage{pxfonts}
\usepackage{eulervm}

\newif\ifcolored
\coloredtrue

% fonts
\usepackage[
  activate={true,nocompatibility},
  tracking=true
]{microtype}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem*{remark*}{Remark}
\numberwithin{equation}{section}

\ifcolored
  \def\IModeColorName{MidnightBlue}
  \def\OModeColorName{Maroon}
\else
  \def\IModeColorName{Black}
  \def\OModeColorName{Black}
\fi

@@

\ifcolored
  \bigskip
  \begin{remark*}[Typographical Conventions]
    In this paper, we hint at the \emph{modes} of judgments and assertions
    \cite{harper:2016} using colors, marking inputs with
    $\IMode{\texttt{blue}}$ and outputs with $\OMode{\texttt{red}}$. As a rule
    of thumb, inputs are things which are supplied when checking the
    correctness of a judgment, and outputs are things which are synthesized in
    the process.
  \end{remark*}
\fi

@@

\newcommand\RefinesCtxNil{\sqsubset^\star_{\mathtt{nil}}}
\newcommand\RefinesCtxSnoc{\sqsubset^\star_{\mathtt{snoc}}}

@@

% TODO: define maps of refined contexts, then change weakening lemma to
% monotonicity, which is stronger and more useful.
\begin{thm}[Weakening]
  If $\Refines{\Phi}{\phi}{\tau}$, then $\Refines{\Phi,u:\psi}{\phi}{\tau}$ (supposing
  $\NotIn{u}{\Dom\Phi}$ and $\Refines{\Phi}{\psi}{\sigma}$).
\end{thm}
\begin{proof}
  This follows trivially from the rule $\RefinesCtxSnoc$ and the canonical renaming
  $\Upsilon\hookrightarrow\Upsilon,u:\sigma$.
\end{proof}
